\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-29 Proposal.tex
update to abstract and intro

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{flushright}
    \includegraphics[scale=1.0]{Logo}
  \end{flushright}
  \vspace{20mm}
  \begin{center}
    \huge
    \textbf{Visualization of Theory Graphs of Semantically Annotated Documents in the Form of Spatial Presentations}
  \end{center}
  \vspace*{4mm}
  \begin{center}
   \Large by
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \Large
    \textbf{Naomi Pentrel}
  \end{center}
  \vspace*{20mm}
  \begin{center}
    \large
    Bachelor Thesis Proposal in Computer Science
  \end{center}
  \vfill
  \begin{flushright}
    \large
    \begin{tabular}{l}

@@

 \section*{Abstract}
Visualization of knowledge is important to foster learning. To optimize the visualization of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context. This research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics. This form of presenting the knowledge should make it easy to examine materials that form the basis for the topics the audience is interested in.\\

Consider the typical lecture one attends as a student. Towards the end of the lecture students might have difficulties remembering earlier topics. When introducing a new topic it would be ideal to have a simple way to find the knowledge dependencies and present students with a simple way to catch up.\\

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims to visualize the connections of some of what is written about Mathematics or other fields in a way that allows students to learn the concepts the current topic depends on should they require to refresh their memories. As such it will foster learning and could transform how we interact with course material as a whole. It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\

@@

The Semantic Web \cite{BernersLee:tsw98} approach aims to transform the World Wide Web (WWW) from a web of mere human readable information to an information web that is processable by machines. There is an interesting similarity in other fields such as that of new presentation tools that aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information and through providing context elevate pure information that is provided to knowledge.\\

These two developments have more in common than one would think. Looking at the history of the WWW, the era of Web 2.0, where everyone is now able to generate content lead to a lot of information but comparatively little knowledge \cite{Weller:npentrel14}. Here the processing of information to provide knowledge is lacking. Similarly I would argue that the existence of tools like Powerpoint have lead to virtually everyone doing presentations. As everyone who has witnessed many presentations knows, these are easily compared to blogs: they contain some knowledge but are often badly delivered and lack structure and context.\\

Semantic Web is aiming to change the former, whereas new, more visual presentation tools provide a solution to help provide presentations that are easier to process and thus will facilitate knowledge transfer. The work proposed here intends to bridge the gap and provide a tool for contextual visualization of information. It adapts some of the concepts of the semantic web on a smaller scale.\\

We want to go from merely displaying information to visualizing information to provide knowledge by displaying the network/context a piece of information is in. In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e. context the information is in.\\

\ednote{INSERT GRAPH that leads from info to knowledge}
\cite{ProbstRaubRomhardt}

"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer.  Thus, we will examine how visually representing information and its context can make knowledge transfer easier. For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information. We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.\\

To exemplify this: Annie, a young student learning Math is watching her teacher give a presentation on how to use the Pythagorean theorem. She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already know how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information, i.e. the Pythagorean theorem depends on knowledge of squares, lengths, area calculation, angles, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was looking at at the time. Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole. \\

\ednote{-addresses fellow experts from your field (but not from your particular topic of research). }
\ednote{- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.}
\ednote{Why is this important for the world? How will this improve learning? ->More effective education. }
\ednote{(target size: 1 page)}
\ednote{http://rhizomik.net/html/~roberto/thesis/html/KnowledgeRepresentation.html}
\ednote{link}
% http://reader.eblib.com/(S(gkwt4h53aadjotp03mi25zsi))/Reader.aspx?p=655998&o=1706&u=tkyUhRRU8oBFV92xtGUdWNHfafo%3d&t=1416427415&h=AAEABAAD4041366D9CC8528AF618690B20349073&s=31025691&ut=5736&pg=1&r=img&c=-1&pat=n&cms=-1&sd=2
\ednote{use Knowledge Presentation System}
\ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn. question: how does the spatial narrative work - should we use the inherent semantic closeness
}
\section{Preliminaries}
To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution. While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.\\

@@

@@

\section{Evaluation Criteria}

\ednote {- work out concepts not a binding contract.}
\ednote{ 1. - 2. system goals -> kinda measurable}
\ednote{ 3.-5. cognitive goals -> exploring space of information systems}

>>>>

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{flushright}
    \includegraphics[scale=1.0]{Logo}
  \end{flushright}
  \vspace{20mm}
  \begin{center}
    \huge
    \textbf{The Combination of Spatial Narrative and Semantic Closeness to derive Visualizations of Theory Graphs}
  \end{center}
  \vspace*{4mm}
  \begin{center}
   \Large by
  \end{center}
  \vspace*{4mm}
  \begin{center}
    \Large
    \textbf{Naomi Pentrel}
  \end{center}
  \vspace*{20mm}
  \begin{center}
    \large
    Bachelor Thesis Proposal in Computer Science
  \end{center}
  \vfill
  \begin{flushright}
    \large
    \begin{tabular}{l}

@@

 \section*{Abstract}
Visualization of knowledge is important to foster learning. To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context. The proposed research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge should enable users to examine materials they may have forgotten which form the basis for the understanding of the topics the audience is interested in.\\

Consider the typical lecture one attends as a student. Towards the end of the lecture students might have difficulties remembering earlier topics. When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with a simple way to catch up.\\

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims to visualize the connections of Mathematical knowledge in a way that allows students to learn the concepts the current topic depends on should they need to refresh their memories. As such it will foster learning and could transform how we interact with course material as a whole. This research has many other real world applications, namely, anywhere where knowledge is supposed to be transferred.\\

@@

The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. There are an interesting similar developments in other fields such as that of new presentation tools. These aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information and through providing context to elevate pure information to knowledge.\\

The concept behind these two developments is quite similar. Looking at the history of the WWW, specifically at the era of Web 2.0 \cite{Weller:npentrel14}, we notice that the web changed from an entity that only few people could add information to, to an entity that enables everyone to generate content. Whereas this lead to a lot of information on the web, it provided comparatively little knowledge. Here the processing of information to provide knowledge is lacking. Similarly the existence of tools like Powerpoint have lead to virtually everyone doing presentations in this format. As everyone who has witnessed many of these presentations knows, these are often easily compared to blogs: they contain some pieces of information but are often badly delivered and lack structure and context. \\

In essence, both issues stem from information being generated without enough context or structure. This makes the information hard to process by humans and/or machines. The Semantic Web hopes to change the former, whereas new, more visual presentation tools using spatial narrative, provide a framework for the creation of presentations that are easier to process for humans and thus facilitate knowledge transfer. The work proposed here intends to provide a tool for automatic contextual visualization of information through the usage of spatial narrative and semantic closeness of information. It adapts some of the concepts of the semantic web on a smaller scale.\\

\begin{center}
\includegraphics[scale=0.5]{model}
\end{center}

"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer. The above graph is based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}. It shows the path from mere data to knowledge through adding context such that we gain information and then through adding networking to get knowledge.\\
\newpage
We want to go from merely displaying information to visualizing information by displaying the network/context a piece of information is in. In this we will not try to semantically represent the meaning of the information that is shown but rather on showing the network, i.e. the context the information is in. Specifically we want to examine whether spatial narrative can be combined with inherent semantic closeness of different pieces of information to facilitate knowledge transfer.\\

To achieve this goal, we intend to create a knowledge presentation system \sys to visually present information and its context (and networks). For this we will be using the OMDoc (Open Mathematical Documents) format which will provide us with an annotated set of documents. This will give us information about the semantic closeness of different pieces of information. From there on we will visualize the dependencies of the information contained in these documents. Of course we will not visualize the dependencies as a simple graph but use the approach of spatial narrative in the form of an API such as Impress.js to allow for us to show the current piece of information of interest within the network of dependent information.\\

To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem. She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information, i.e. the Pythagorean theorem depends on knowledge of squares, lengths, area calculation, angles, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

After reading this contrived story, I leave the reader to think about examples in his or her own life where he or she would have appreciated having the context of the information he or she was learning at the time. Many of these stories exist in real life and it is therefore important to provide this context to facilitate learning and knowledge transfer as a whole. \\

\section{Preliminaries}
To understand the problem of information that lacks context, this part will provide the necessary background information to allow us to derive a possible solution. While doing so it will demonstrate why this research is important and how it will improve the transfer of knowledge.\\

@@

\subsection{Terminology}
Information 
Knowledge
Context.

@@

\section{Evaluation Criteria}
\ednote {KEEP - real question: does spatial narrative work together with inherent semantic closeness -cogn. question: how does the spatial narrative work - should we use the inherent semantic closeness
}
\ednote {- work out concepts not a binding contract.}
\ednote{ 1. - 2. system goals -> kinda measurable}
\ednote{ 3.-5. cognitive goals -> exploring space of information systems}
